Think deep for reef resilience

### 2025-07-22 paper/paper_draft.qmd
Reinstate DHW-tolerance content into paper and ensure figs match results

Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the GBR were
obtained from the HighResCoralStress database [@dixon2022; @dixon2023]. Maximum monthly mean
DHW levels were calculated from the SST data following NOAA methodology [@liu2017;
@skirving2020]. DHWs were represented by a selection of five Global Climate Models (GCMs)
from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6; **citation**).
These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4, and
their inclusion were based on evaluation by Grose et al. [-@grose2023]. Grose et al.
[-@grose2023] found these GCMs to rank highly, among 50 GCMs, in recreation of historical atmospheric temperature and precipitation conditions in the Australasian region. While this assessment does not consider oceanic data, Grose et al. [@-grose2023] provide a region-specific selection mechanism which we use as an indicator of general performance of GCMs for the region.

@@

```{=html}
<!-- Across the five GCMs, 50% (1812) of reefs, at management region scale, remain in the same
‘low, medium, high’ cluster assignment. 1757 Reefs (49%) that changed clusters by one level
across the GCMs (e.g. a reef is assigned ‘low’ and ‘medium’ in different GCMs), while 46
(1%) reefs changed clusters by two levels across the GCMs (e.g. a reef is assigned ‘low’ and
‘high’ in different GCMs). -->
```

@@

Correlation between reef total coral cover and reef DHW timeseries decreases as cluster
coral cover decreases, with reefs in the ‘high’ cluster commonly having the greatest total
cover – DHW timeseries correlation levels (@sfig-access-esm1-5-bioregion-dhwcor;
@sfig-access-cm2-bioregion-dhwcor; @sfig-ec-earth3-veg-bioregion-dhwcor;
@sfig-gfdl-cm4-bioregion-dhwcor; @sfig-noresm2-mm-bioregion-dhwcor).

@@

<!-- In some bioregions (4 for ACCESS-ESM1-5) reefs in the ‘low’ cluster have substantially 
lower mean thermal tolerance levels compared to reefs in other clusters. However, many 
bioregions do not show strong differences in thermal tolerance levels 
(@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol; 
@sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol; 
@sfig-noresm2-mm-bioregion-dhwtol). -->

In many bioregions reefs with high area-relative coral cover levels (‘high’ cluster) have
the lowest initial proportions of habitable area occupied by corals, while reefs in the
‘low’ cluster often have the highest initial proportions of coral habitable area occupied by
corals (@sfig-access-esm1-5-bioregion-initialproportion;
@sfig-access-cm2-bioregion-initialproportion;
@sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion;
@sfig-noresm2-mm-bioregion-initialproportion).

@@

Reefs in different clusters largely do not differ in mean modelled DHW levels experienced,
and exhibit overall similar DHW timeseries. While these reefs experience similar magnitude
DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress
events depends on reef depth. Our results suggest that within shallow-water reef ecosystems
(non-mesophotic, depth \< 30m), depth contributes greatly to reef resilience and the ability
of the reef to maintain positive carbonate budgets under future conditions. While similar
findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses
have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
found no association between depth and the alleviation of heat stress across a range of
shallow reefs in the Pacific. Reefs at shallow depths experience no, or few, years with
coral cover exceeding levels likely required to maintain positive carbonate budgets.
Movement of shallow reefs towards negative cabonate budgets under increasing future thermal
stress over time may contribute to phase shifts in reef dominant CaCO~3~ production.
Shifting from coral driven to coralline encrusting algae driven production, or to bioerosion
dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010; @perry2008].
While reefs at increased depths may be able to maintain coral driven CaCO~3~ production and
accumulation into the future for longer.
<!-- The depth refugia found on a reef in turn influences the degree of correlation between coral cover timeseries and DHW levels. Reefs in low and medium clusters have lower levels of cover – DHW correlation than those in high clusters, due to their initial sharp declines in coral cover combined with low depth – refugia in the face of persistently high thermal stress these reefs do not recover post 2030, leaving little ability to decline further in periods of high thermal stress and recover in periods of low thermal stress. -->

@@

Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater
thermal tolerance than reefs in lower coral cover clusters **need to replot tolerance
values**. This is in contrast with literature suggesting corals have the capacity to adapt
to increasing climate change pressures [@humanes2022; @lachs2024], including the
investigation by Bairos-Novak et al. [-@bairos-novak2021] that revealed high heritability of
bleaching and survival response traits used to inform the distributions of thermal tolerance
traits used in this investigation. The lack of influence of thermal tolerance on reef
outcomes is likely due to reef being impacted by overall similar levels of thermal stress,
combined with the greater importance of factors such as reef depth.

It is a strongly held conclusion in coral reef ecology that a primary facet of reef
resilience is the degree of larval connectivity between reefs and the supply of recruits
that a reef receives following disturbance [@hock2017] **expand citations**. It was expected
that resilient reefs would have greater incoming than outgoing larval connectivity to
promote recovery in years following thermal stress, while non-resilient reefs would have
greater outgoing than incoming connectivity inhibiting recruitment of corals post thermal
stress. In contrast, our results suggest that there are few differences between resilient
and non-resilient reefs in connectivity metrics such as the ratio of outgoing to incoming
larval connectivity and total connectivity strength. Furthermore, our results suggest no
relationship between connectivity and the ability of reefs to maintain positive carbonate
budgets under future conditions. There has been contrasting evidence [@bode2018; @hock2017]
surrounding whether recent generation connectivity modelling is able to identify reefs that
are important for recovery processes. A key separation of these investigations is their use
of differing larval connectivity models. Reef depth was not considered in these
investigations of reef network resilience. These investigations were performed using prior
generations of larval connectivity models parameterised for 2008-2013 [@hock2017] and
1996-2002 [@bode2018] time periods. Using updated 1km resolution larval connectivity across
the whole GBR, with a limited temporal sample of particle flows, our results suggest that
larval connectivity alone is not as important for reef resilience and recovery as
environmental refugia from thermal stress such as depth. Our findings may differ due to the
highly uncertain nature of connectivity methods used **citation**, the way larval flows and
juvenile recruitment are implemented in ADRIA - CoralBlox, and the magnitude of early
bleaching events decreasing the breeding capacity of strongly connected reefs. Further
improvements and research in connectivity modelling are necessary to provide a robust
comparison of all factors influencing reef resilience.

@@

Overall, our results suggest that when modelled as part of a large and complex ecosystem,
reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
support of depth as a form of refugia for shallow reefs. While protecting ‘key node’ reefs
in larval connectivity networks is an important consideration for reef restoration efforts
[@anthony2020; @hock2017], our results suggest that resilient reefs do not have greater
incoming or total connectivity to contribute to their resilience under modelled projected
conditions. Instead, we suggest that depth, and likely other environmental thermal refugia
mechanisms contribute greater to overall reef resilience and recovery. We suggest further
analyses that investigate the benefits of incorporating depth-based resilience into reef
decision making.

@@

![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
width="`{julia} ecs_width`" height="500" align="center"}

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW level for each cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
width="`{julia"} violin_width\`"}

```{=html}
<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030
and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest
median area-relative cover between 2030 and 2040 within each bioregion. Solid lines
represent the median DHW tolerance value for each cluster. Displays results for
ACCESS-ESM1-5 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol width="`{julia}
violin_width\`"} -->
```

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for ACCESS-CM2 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for EC-Earth3-Veg GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for GFDL-CM4 GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol width=`{julia} violin_width`} -->

@@

<!-- ![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the median DHW tolerance value for each cluster. Displays results for NorESM2-MM GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol width=`{julia} violin_width`} -->

>>>>

Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the GBR were
obtained from the HighResCoralStress database [@dixon2022; @dixon2023]. Maximum monthly mean
DHW levels were calculated from the SST data following NOAA methodology [@liu2017;
@skirving2020]. DHWs were represented by a selection of five Global Climate Models (GCMs)
from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6; **citation**).
These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4, and
their inclusion were based on evaluation by Grose et al. [-@grose2023]. Grose et al.
[-@grose2023] found these GCMs to rank highly, among 50 GCMs, in recreation of historical
atmospheric temperature and precipitation conditions in the Australasian region. While this
assessment does not consider oceanic data, Grose et al. \[\@-grose2023\] provide a
region-specific selection mechanism which we use as an indicator of general performance of
GCMs for the region.

@@

Comparing across GCMs, it is common for reefs to switch cluster level, including from low to
high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). This is
expected as spatial differences in GCM DHW timeseries result in reefs being impacted in
different magnitudes relative to other reefs in their bioregion.

@@

In many bioregions reefs in the 'low' cover cluster have the lowest cover - DHW timeseries
correlation levels, while reefs in 'high' clusters have the highest correlation levels
(@sfig-access-esm1-5-bioregion-dhwcor; @sfig-access-cm2-bioregion-dhwcor;
@sfig-ec-earth3-veg-bioregion-dhwcor; @sfig-gfdl-cm4-bioregion-dhwcor;
@sfig-noresm2-mm-bioregion-dhwcor).

@@

Similarly, there are no substantial differences between reef clusters in mean thermal
tolerance levels (@sfig-access-esm1-5-bioregion-dhwtol; @sfig-access-cm2-bioregion-dhwtol;
@sfig-ec-earth3-veg-bioregion-dhwtol; @sfig-gfdl-cm4-bioregion-dhwtol;
@sfig-noresm2-mm-bioregion-dhwtol).

There are no consistent differences across bioregions and GCMs between clusters in their
reefs' initial proportion of habitable area occupied by corals
(@sfig-access-esm1-5-bioregion-initialproportion;
@sfig-access-cm2-bioregion-initialproportion;
@sfig-ec-earth3-veg-bioregion-initialproportion; @sfig-gfdl-cm4-bioregion-initialproportion;
@sfig-noresm2-mm-bioregion-initialproportion).

@@

Reefs in different clusters largely do not differ in mean modelled DHW levels experienced,
and exhibit overall similar DHW timeseries. While these reefs experience similar magnitude
DHWs based on SST, the proportion of the reefs' coral population impacted by heat stress
events depends on reef depth. Our results suggest that within shallow-water reef ecosystems
(non-mesophotic, depth \< 30m), depth contributes greatly to reef resilience and the ability
of the reef to maintain positive carbonate budgets under future conditions. While similar
findings have been demonstrated in the eastern Pacific [@smith2014], depth refugia analyses
have often focussed on the potential of mesophotic reefs (\> 30m deep) as thermal refugia
[@bongaerts2010; @holstein2015; @semmler2017]. In contrast, Venegas et al. [-@venegas2019]
found no association between depth and the alleviation of heat stress across a range of
shallow reefs in the Pacific. Reefs at shallow depths experience no, or few, years with
coral cover exceeding levels likely required to maintain positive carbonate budgets.
Movement of shallow reefs towards negative cabonate budgets under increasing future thermal
stress over time may contribute to phase shifts in reef dominant CaCO~3~ production.
Shifting from coral driven to coralline encrusting algae driven production, or to bioerosion
dominated systems with rapid erosion of physical reef frameworks [@dudgeon2010; @perry2008].
While reefs at increased depths may be able to maintain coral driven CaCO~3~ production and
accumulation into the future for longer.

@@

Overall, our findings do not suggest that reefs in ‘high’ cover clusters have greater
thermal tolerance than reefs in lower coral cover clusters. This is in contrast with
literature suggesting corals have the capacity to adapt to increasing climate change
pressures [@humanes2022; @lachs2024], including the investigation by Bairos-Novak et al.
[-@bairos-novak2021] that revealed high heritability of bleaching and survival response
traits, used to inform the distributions of thermal tolerance traits used in this
investigation. The lack of influence of thermal tolerance on reef outcomes is likely due to
reefs being impacted by high levels of thermal stress early in timeseries and being unable
to build thermal tolerance to DHW levels greater than 9°C.

It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
the degree of larval connectivity between reefs and the supply of recruits that a reef
receives following disturbance [@hock2017] **expand citations**. In contrast, our results
suggest that there are few differences between resilient and non-resilient reefs in
connectivity metrics such as the ratio of outgoing to incoming larval connectivity and total
connectivity strength. Furthermore, our results suggest no relationship between connectivity
and the ability of reefs to maintain positive carbonate budgets under future conditions.
There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent
generation connectivity modelling is able to identify reefs that are important for recovery
processes. A key separation of these investigations is their use of differing larval
connectivity models. Reef depth was not considered in these investigations of reef network
resilience. These investigations were performed using prior generations of larval
connectivity models parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time
periods. Using updated 1km resolution larval connectivity across the whole GBR, with a
limited temporal sample of particle flows, our results suggest that larval connectivity
alone is not as important for reef resilience and recovery as environmental refugia from
thermal stress such as depth. Our findings may differ due to the highly uncertain nature of
connectivity methods used **citation**, the way larval flows and juvenile recruitment are
implemented in ADRIA - CoralBlox, and the magnitude of early bleaching events decreasing the
breeding capacity of strongly connected reefs. Further improvements and research in
connectivity modelling are necessary to provide a robust comparison of all factors
influencing reef resilience.

@@

Overall, our results suggest that when modelled as part of a large and complex ecosystem,
reef depth is a key factor contributing to ongoing reef resilience. We provide evidence in
support of depth as a form of refugia for shallow reefs. While protecting ‘key node’ reefs
in larval connectivity networks is an important consideration for reef restoration efforts
[@anthony2020; @hock2017], our results suggest that current connectivity modelling methods
are not able to generate connectivity levels that contribute to reef resilience under
projected conditions. We suggest further analyses that investigate the benefits of
incorporating depth-based resilience into reef decision making, as well as further research
and development in connectivity modelling methods for whole-ecosystem scales.

@@

![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
width="`{julia} ecs_width`" align="center"}

![Heatmaps indicating reef cluster assignments within each bioregion across the five GCMs.
Green indicates a low cover cluster assignemnt, orange represents a medium cover assignment
and blue represents assignment of a reef to a high coral cover cluster. The vertical width
of reef elements varies depending on the number of reefs within the bioregion (displayed in
the y axis). The x axis represents the different GCM levels (EC-Earth3-Veg, ACCESS-ESM1-5,
ACCESS-CM2, NorESM2-MM and
GFDL-CM4).](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_bioregion_cluster_assignment.png){#fig-gcm-bioregion-cluster-assignment
width="`{julia} timeseries_width`"}

@@

![Mean timeseries DHW values for reefs within each bioregion, separated into clusters
assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest
median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters
(orange) are clusters with intermediate median area-relative cover between 2030 and 2040
within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW level for each cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/mean_dhw_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwmean
width="`{julia} violin_width`"}

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW tolerance value for each cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-esm1-5-bioregion-dhwtol
width="`{julia} violin_width`"}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW tolerance value for each cluster. Displays results for ACCESS-CM2
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-CM2/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-access-cm2-bioregion-dhwtol
width="`{julia} violin_width`"}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW tolerance value for each cluster. Displays results for EC-Earth3-Veg
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/EC-Earth3-Veg/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-ec-earth3-veg-bioregion-dhwtol
width="`{julia} violin_width`"}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW tolerance value for each cluster. Displays results for GFDL-CM4
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/GFDL-CM4/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-gfdl-cm4-bioregion-dhwtol
width="`{julia} violin_width`"}

@@

![Mean timeseries DHW tolerance value for reefs within each bioregion, separated into
clusters assigned by timeseries clustering. ‘Low’ clusters (green) are clusters with the
lowest median area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’
clusters (orange) are clusters with intermediate median area-relative cover between 2030 and
2040 within each bioregion. ‘High’ clusters (blue) are clusters with the highest median
area-relative cover between 2030 and 2040 within each bioregion. Solid lines represent the
median DHW tolerance value for each cluster. Displays results for NorESM2-MM
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/NorESM2-MM/bioregion/dhw_tolerance_bioregion_violin.png){#sfig-noresm2-mm-bioregion-dhwtol
width="`{julia} violin_width`"}
